Scaling of Electrode-Electrolyte Interface Model Parameters In Phosphate Buffered Saline

### 2014-02-11 paper.tex
Lingering changes

This displacement mechanism is capable of transferring charge between electrical and biological systems without damaging electrodes or tissue. \cite{Horch2004}
This behaviour is modelled by way of a Constant Phase Element (CPE); also known as a fractional capacitor.
}
{
    \color{blue}
For simulation purposes this element is realised as an array of R-C branches.~\cite{ScottSingle2013,Morrison59,Elwakil10} where the value of each R-C pair is chosen to set the slope of impedance relative to frequency. The placement of R-C pairs within the CPE is determined by Morrison's parameters $m$ and $k$, where $k$ determines the spacing, or density, of R-C branches and $m$ determines the resulting slope.
}
We measure displacement currents by sweeping the frequency of a sinusoidal stimulus across electrodes 2 and 7 of the Octrode while measuring the voltage between electrodes 2 and 3 (numbering shown in Fig.~\ref{fig:octrode}). 
This allows for the measurement of a single interface impedance in series with the resistance presented by the bulk solution. 
\begin{figure}
    \begin{center}
        \includegraphics{graphics/chargeInjectionVsFrequency_magnitude}
    \end{center}
    \caption{\color{blue} Charge injected per phase during CPE measurement for each of the six concentrations of PBS. Calculated using a geometric surface area of 10\thinspace mm$^{2}$}
    \label{fig:chargeInjectionVsFrequency}
\end{figure}
{
    \color{blue}
    The geometric current density during measurements peaked at 22.59\thinspace mA/cm$^{2}$ at 5300\thinspace kHz in 1.0X PBS and fell as low as 27.66\thinspace $\mu$A/cm$^{2}$ at 50\thinspace mHz in 0.025X PBS. Charge injection per phase is shown in figure~\ref{fig:chargeInjectionVsFrequency} for each solution. 
The stimulus waveform was set at 300\thinspace mV (peak) at each measurement point. The measurement instruments used are the same as those used to measure the inter-electrode resistance.
}
{
    \color{blue}
Figure~\ref{fig:CPE_Magnitude} shows the magnitude of the measured response of each of the six PBS concentrations accompanied by simulation results. Figure~\ref{fig:CPE_Phase} shows the phase response for the same measurements, again with the simulated response at each concentration. The simulated responses are generated using the optimised parameter values presented in Table~\ref{tab:CPEparams}. Those values were chosen as they give the closest match to the measured data.
}
As shown in the interface model schematic (figure~\ref{fig:schematic}), the interface contains its own internal series resistance ($R_{S}$). The resistance seen in series with the CPE will therefore be the sum of both the resistance due to the bulk resistivity of the fluid and $R_{S}$, to which we will refer as $R_{S+bulk}$.
In figure~\ref{fig:CPE_Magnitude}, the slope and magnitude of the CPE are visible below 1\thinspace Hz whereas $R_{S+bulk}$  dominates above 1\thinspace kHz; it is clear that the two do not scale similarly.
As the impedance of the CPE and $R_{S+bulk}$ are separable with frequency, these measurements can be used to determine the CPE parameters and $R_{S}$.

@@

We now test the claim that 0.1X PBS is a reasonable representation of the spine of a living sheep.
The displacement measurements were repeated inside the spinal canal of a live sheep, just outside the dura as shown in figure~\ref{fig:sheepSpine}. The sheep were prepared and anaesthetised using the procedures described in \cite{Parker2013} under the Animal Care and Ethics Committee approval of the Royal North Shore Hospital. The study complied with the Australian Code of Practice for the Care and Use of Animals for Scientific Purposes.
{\color{blue} Four measurements taken at regular invervals over a period of 30 minutes} are presented in figures~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase} on top of the array of traces for saline taken from figures~\ref{fig:CPE_Magnitude} and~\ref{fig:CPE_Phase}.
Although it is clear that there are complications in vivo, a 0.25X PBS saline offers a good approximation to the resistive part of the trace.
The reactive part would be better modelled by a solution of less than 0.025X concentration.

\begin{figure}
    \begin{center}
        \includegraphics{graphics/displacement-withSheep_impedanceVsFrequency_magnitude}
    \end{center}
    \caption{Comparison between the magnitude of CPE in live sheep {\color{blue}(blue error bars)} against each of the PBS traces from figure~\ref{fig:CPE_Magnitude} (grey lines) and a simulated fit to the sheep data (red trace).}
    \label{fig:displacement_sheepCPEMagnitude}
\end{figure}

\begin{figure}
    \begin{center}
        \includegraphics{graphics/displacement-withSheep_impedanceVsFrequency_phase}
    \end{center}
    \caption{Comparison between the phase response of the CPE in live sheep {\color{blue}(blue error bars)} against each of the PBS traces taken from figure~\ref{fig:CPE_Phase} (grey lines) and a simulated fit to the sheep data (red trace).}
    \label{fig:displacement_sheepCPEPhase}
\end{figure}

@@

page 2, in text/ table II. The scaling parameters and their meanings should be described more comprehensively. They remain somewhat unclear and meaningless to reader.\\
{\color{OliveGreen}
    Item 9\\
    We have encouraged the reader to review ScottSingle2013 in order to understand the interpretation of the given parameters. 
}\\

@@

page 2, line 52. "the magnitude shifts relatively little". However, In Fig. 4, logaritmic scale is used, and the change from 1.0X to 0.025X is almost 50k at the lowest frequencies. 
please clarify this point.\\
{\color{OliveGreen}
    Item 12\\
    Have reworded this slightly to convey that the shift in the CPE response is small relative to the shift in the resistance in the solution bulk. We are referring to a relative difference, a gain in conductivity as a factor of the current conductivity.
    {\color{red} Help! I don't know how better to explain this, The difference between 9 000 000 and 1 000 000 000 is small compared to the difference between 20 and 2000}
}\\

@@

Finally, and most importantly, the part of in vivo measurements are very limited since only one spinal channel measurement has been performed. My opinion is that this manuscript could be even better without this uncertain (n=1) result and thus I recommend to leave this part out.\\
{\color{OliveGreen}
    Item 16\\ 
    Graph of sheep response to displacement stimulus has been updated to include four separate measurements taken on the second day of sheep measurement. The first day gave results typical of these but we ran into connection problems leading to intermittent data hence they have been omitted.
}\\
}

@@

9. P3, col 2, line 31: why 2 and 6?\\
{\color{OliveGreen}
    Item 28\\
    The mention of the use of electrodes 2 and 6 was a mistake. We actually used electrodes 3 and 7 due to damage to the electrode array we were using. See updated explination on page 4.
}\\

@@

Overall, the paper was brief and to the point, which in this case is actually a determent instead of a benefit. Much of the underlying theory and development of parameters appear without informing the reader of their purpose or how they were calculated and/or measured. 
For example, the parameters in Table 2 (and reported to be in Figure 3) are not explained and what their relationship to the remainder of the manuscript is not provided. 
{\color{OliveGreen}
    Item 34\\
    {\color{Red} Explain parameters in table two better or refer readers to ScottSingle2013}
    No response yet.
}
To make this manuscript more approachable to a wider audience, I recommend the authors more fully develop Sections II, III, and IV. Further, they should explain their testing in terms of standard electrochemical characterization, detailing their counter, working, and reference electrodes used in measuring impedance. 
{\color{OliveGreen}
    Item 35\\
    {\color{Red} Try to include any relevant electrochemical information, find out what that is first}
    No response yet.
}
As part of this expansion, the references should be increased beyond the present ten references. Although their current references include clearly important electrode characterization references (Cogan, Merrill et. al, \& Kane et. al), the information contained in these references are not effectively used to support the authors’ work.\\
{\color{OliveGreen}
    Item 36\\
    {\color{Red} Perhaps Troyk could be added. References have been extended to include a Masters Theses and Neuroprosthetics: Theory and practise book}
}

>>>>

This displacement mechanism is capable of transferring charge between electrical and biological systems without damaging electrodes or tissue. \cite{Horch2004}
This behaviour is modelled by way of a Constant Phase Element (CPE); also known as a fractional capacitor.
}
{
    \color{blue}
For simulation purposes this element is realised as an array of R-C branches.~\cite{ScottSingle2013,Morrison59,Elwakil10} where the value of each R-C pair is chosen to set the slope of impedance relative to frequency. The placement of R-C pairs within the CPE is determined by Morrison's parameters $m$ and $k$, where $k$ determines the spacing, or density, of R-C branches and $m$ determines the resulting slope.
}
We measure displacement currents by sweeping the frequency of a sinusoidal stimulus across electrodes 2 and 7 of the Octrode while measuring the voltage between electrodes 2 and 3 (numbering shown in Fig.~\ref{fig:octrode}). 
This allows for the measurement of a single interface impedance in series with the resistance presented by the bulk solution. 
\begin{figure}
    \begin{center}
        \includegraphics{graphics/chargeInjectionVsFrequency.pdf}
    \end{center}
    \caption{\color{blue} Charge injected during CPE measurement for each of the six concentrations of PBS. Calculated using an effective surface area of 14\thinspace mm$^{2}$}
    \label{fig:chargeInjectionVsFrequency}
\end{figure}
{
    \color{blue}
Current density during measurements peaked at $11.5\thinspace A/m^{2}$ at 10\thinspace kHz in 1.0X PBS and fell as low as $0.0141\thinspace A/m^{2}$ at 50\thinspace mHz in 0.025X PBS. The charge injected is shown in figure~\ref{fig:chargeInjectionVsFrequency}. 
The stimulus waveform was set at 300\thinspace mV (peak) at each measurement point. The measurement instruments used are the same as those used to measure the inter-electrode resistance.
}
{
    \color{blue}
Figure~\ref{fig:CPE_Magnitude} shows the magnitude of the measured response of each of the six PBS concentrations accompanied by simulation results. Figure~\ref{fig:CPE_Phase} shows the phase response for the same measurements, again with the simulated response at each concentration. The simulated responses are generated using the optimised parameter values presented in Table~\ref{tab:CPEparams}. Those values were chosen as they give the closest match to the measured data.
}
As shown in the interface model schematic (figure~\ref{fig:schematic}), the interface contains its own internal series resistance ($R_{S}$). The resistance seen in series with the CPE will therefore be the sum of both the resistance due to the bulk resistivity of the fluid and $R_{S}$, to which we will refer as $R_{S+bulk}$.
In figure~\ref{fig:CPE_Magnitude}, the slope and magnitude of the CPE are visible below 1\thinspace Hz whereas $R_{S+bulk}$  dominates above 1\thinspace kHz; it is clear that the two do not scale similarly.
As the impedance of the CPE and $R_{S+bulk}$ are separable with frequency, these measurements can be used to determine the CPE parameters and $R_{S}$.

@@

We now test the claim that 0.1X PBS is a reasonable representation of the spine of a living sheep.
The displacement measurements were repeated inside the spinal canal of a live sheep, just outside the dura as shown in figure~\ref{fig:sheepSpine}. The sheep were prepared and anaesthetised using the procedures described in \cite{Parker2013} under the Animal Care and Ethics Committee approval of the Royal North Shore Hospital. The study complied with the Australian Code of Practice for the Care and Use of Animals for Scientific Purposes. The measurements are presented in figures~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase} on top of the array of traces for saline taken from figures~\ref{fig:CPE_Magnitude}
and~\ref{fig:CPE_Phase}.
Although it is clear that there are complications in vivo, a 0.25X PBS saline offers a good approximation to the resistive part of the trace.
The reactive part would be better modelled by a solution of less than 0.025X concentration.

\begin{figure}
    \begin{center}
        \includegraphics{graphics/displacement-withSheep_impedanceVsFrequency_magnitude}
    \end{center}
    \caption{Comparison between the magnitude of CPE in live sheep (blue circles) against each of the PBS traces from figure~\ref{fig:CPE_Magnitude} (grey lines) and a simulated fit to the sheep data (red trace).}
    \label{fig:displacement_sheepCPEMagnitude}
\end{figure}

\begin{figure}
    \begin{center}
        \includegraphics{graphics/displacement-withSheep_impedanceVsFrequency_phase}
    \end{center}
    \caption{Comparison between the phase response of the CPE in live sheep (blues circles) against each of the PBS traces taken from figure~\ref{fig:CPE_Phase} (grey lines) and a simulated fit to the sheep data (red trace).}
    \label{fig:displacement_sheepCPEPhase}
\end{figure}

@@

page 2, in text/ table II. The scaling parameters and their meanings should be described more comprehensively. They remain somewhat unclear and meaningless to reader.\\
{\color{OliveGreen}
    Item 9\\
    We have encouraged the reader to review ScottSingle2013 in order to understand the interpretation of the given parameters. {\color{red} Should I just say they are resistances of elements in a resistor mesh?}
}\\

@@

page 2, line 52. "the magnitude shifts relatively little". However, In Fig. 4, logaritmic scale is used, and the change from 1.0X to 0.025X is almost 50k at the lowest frequencies. 
please clarify this point.\\
{\color{OliveGreen}
    Item 12\\
    This has been reworded to improve clarity, see end of section III. We are referring to relative shifts as opposed to absolute impedances.
}\\

@@

Finally, and most importantly, the part of in vivo measurements are very limited since only one spinal channel measurement has been performed. My opinion is that this manuscript could be even better without this uncertain (n=1) result and thus I recommend to leave this part out.\\
{\color{OliveGreen}
    Item 16\\ 
    {\color{Red} Leave sheep in but perhaps show the second measurement (day 1) if possible (4th reviewer found sheep correlation to PBS result interesting). Would a separate sheep measurement graph be of use showing all sheep results? Jonathans response: Put more sheep data in, put some error bars on.}
    No response yet.
}\\
}

@@

9. P3, col 2, line 31: why 2 and 6?\\
{\color{OliveGreen}
    Item 28\\
    {\color{Red} Took resistance measurements of lead and electrode 2 is open circuit inside the electrode. Must have meant 3 and 7, due to damaged electrode 2}
    No response yet.
}\\

@@

Overall, the paper was brief and to the point, which in this case is actually a determent instead of a benefit. Much of the underlying theory and development of parameters appear without informing the reader of their purpose or how they were calculated and/or measured. 
For example, the parameters in Table 2 (and reported to be in Figure 3) are not explained and what their relationship to the remainder of the manuscript is not provided. 
{\color{OliveGreen}
    Item 34\\
    {\color{Red} Explain parameters in table two better or refer readers to ScottSingle2013}
    No response yet.
}
To make this manuscript more approachable to a wider audience, I recommend the authors more fully develop Sections II, III, and IV. Further, they should explain their testing in terms of standard electrochemical characterization, detailing their counter, working, and reference electrodes used in measuring impedance. 
{\color{OliveGreen}
    Item 35\\
    {\color{Red} Try to include any relevant electrochemical information, find out what that is first}
    No response yet.
}
As part of this expansion, the references should be increased beyond the present ten references. Although their current references include clearly important electrode characterization references (Cogan, Merrill et. al, \& Kane et. al), the information contained in these references are not effectively used to support the authors’ work.\\
{\color{OliveGreen}
    Item 36\\
    {\color{Red} Perhaps Troyk could be added. A search for textbook knowledge and more published state of the art should uncover more references}
    No response yet.
}\\
